Fusion Moves for Correlation Clustering

### 2014-11-13 paper/egpaper_for_review.tex
update 4.1 including figures

Instead of problem~\ref{eq:fusion_move_a} we can now solve problem~\ref{eq:edgeproblem} on the contracted graph $G_{\breve{y}}$.
This is, depending on the intersection of the current and proposed solution, magnitudes smaller than $G$.
The correlation clustering problem on $G_{\breve{y}}$ can be solved by any correlation clustering solver.
Since $G_{\breve{y}}$ is smaller exact methods or good approximative methods like 
multicuts~\cite{kappes_2013_arxiv} or CGC~\cite{beier_2014_cvpr}
become tractable.

>>>>

Instead of problem~\ref{eq:fusion_move_a} we can now solve problem~\ref{eq:edgeproblem} on the contracted graph $G_{\breve{y}}$.
This is, depending on the intersection of the current and proposed solution, magnitudes smaller than $G$.
The correlation clustering problem on $G_{\breve{y}}$ can be solved by any correlation clustering solver.
Since $G_{\breve{y}}$ is smaller exact methods or good approximative methods like 
multicuts~\cite{kappes_2013_arxiv} or CGC~\cite{beier_2014_cvpr}
are very fast.
